Constraining the Interiors of Asteroids Through Close Encounters

### 2022-04-01 paper/main.tex
Updated density to make it faster

The recent increase in the quantity and quality of high-sensitivity, all-sky surveys, such as the Wide-field Infrared Survey Explorer (WISE) mission \cite{wright2010wide} has prompted the discovery of numerous asteroids, some kilometer-sized, and some predicted to encounter Earth or other planets closely in the near future. Theoretical work has demonstrated that many of these asteroids incur altered rotational velocities due to tidal torque \cite{paul88, SCHEERES2000106, ashenberg07, BOUE2009750, HouMar2017}; this two-body generalized system has been studied to several orders and with several different methods. The angular velocity changes induced by tidal torque occur both in asteroid binaries \cite{Naidu_2015}, and during planetary encounters \cite{RICHARDSON199847, scheeres2004evolution}. Such asteroids need not be tidally disrupted for their rotation state to be perturbed by tidal torque. Some examples of altered rotational velocity have recently been observed, including for (367943) Duende \cite{MOSKOVITZ2020113519, benson2020spin}, and have been predicted for the 2029 encounter of (99942) Apophis with Earth \cite{SCHEERES2005281}. Altered rotational states have been excluded for 1I/2017 U1 'Oumuamua \cite{KWIECINSKI2018170}.

>>>>

The recent increase in the quantity and quality of high-sensitivity, all-sky surveys, such as the Wide-field Infrared Survey Explorer (WISE) mission \cite{wright2010wide} has prompted the discovery of numerous asteroids, some kilometer-sized, and some predicted to encounter Earth or other planets closely in the near future. Theoretical work has demonstrated that many of these asteroids incur altered rotational velocities due to tidal torque \cite{paul88, SCHEERES2000106, ashenberg07, BOUE2009750, HouMar2017}; this two-body generalized system has been studied to several orders and with several different methods. The angular velocity changes induced by tidal torque occur both in asteroid binaries \cite{Naidu_2015}, and during planetary encounters \cite{RICHARDSON199847, scheeres2004evolution}. Such asteroids need not be tidally disrupted for their rotation state to be perturbed by tidal torque. Some examples of altered rotational velocity have recently been observed, including for (367943) Duende \cite{MOSKOVITZ2020113519, benson2020spin}, and have been predicted for the 2029 encounter of (99942) Apophis with Earth \cite{SCHEERES2005281, DEMARTINI201993}. Altered rotational states have been excluded for 1I/2017 U1 'Oumuamua \cite{KWIECINSKI2018170}.
